Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-01 submission/NatCom_appendix.tex
put all those figs in appendix

To explain further how to reproduce our analysis, we run three batches of linear regressions. 
First, at the global level, we divide models by datasets and run regressions separately on all models of a certain dataset, regardless of the architecture. 
At this level, the plots are quite noisy and clustered, as each architecture has its own accuracy trend; but one can
 still see that most plots show positive relationship with positive coefficients. 
% V1 REMOVED FOR V2 % Example regressions are shown in Figure~\ref{fig:DSalphas}, as available in the results notebook.
Example regressions are shown in 
Figure~\ref{fig:DSalphas}, for models segmented by dataset, as listed in Table~\ref{table:datasets}, 
and in 
Figure~\ref{fig:ARCHalphas}, for models segmented by architecture, as listed in Table~\ref{table:architectures}.
\michael{Comment here on differences.}

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
See Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.

@@

@@

\begin{figure}[t]
    \centering
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_01}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_02}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_03}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_04}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_05}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_06}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_07}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_08}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_09}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_10}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_11}
    }
    \subfigure[ XXX, XXX ]{
        \includegraphics[width=3.7cm]{img/hex.png}
        \label{fig:summary_regressions_A_12}
    }
    \caption{Regression plots for model-dataset pairs, based on data from Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
             Each row corresponds to a different dataset-model pair:
             imagenet-1k and ResNet; 
             imagenet-1k and EfficientNet; and 
             imagenet-1k and PreResNet, repsectively.
             Each column column corresponds to a different metric:
             $\langle\log\Vert\cdot\Vert_{F}\rangle$; 
             $\langle\log\Vert\cdot\Vert_{\infty}\rangle$; 
             $\hat{\alpha}$; and
             $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$, repsectively.
            }
    \label{fig:summary_regressions_A}
\end{figure}

>>>>

To explain further how to reproduce our analysis, we run three batches of linear regressions. 
First, at the global level, we divide models by datasets and run regressions separately on all models of a certain dataset, regardless of the architecture. 
At this level, the plots are quite noisy and clustered, as each architecture has its own accuracy trend; but one can
 still see that most plots show positive relationship with positive coefficients. 
% V1 REMOVED FOR V2 % Example regressions are shown in Figure~\ref{fig:DSalphas}, as available in the results notebook.
%%Example regressions are shown in 
%%Figure~\ref{fig:DSalphas}, for models segmented by dataset, as listed in Table~\ref{table:datasets}, 
%%and in 
%%Figure~\ref{fig:ARCHalphas}, for models segmented by architecture, as listed in Table~\ref{table:architectures}.
\michael{Comment here on differences.}

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
\michael{Mention KTau.}
See Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.

See
Figure~\ref{fig:summary_regressions_A},
Figure~\ref{fig:summary_regressions_B},
Figure~\ref{fig:summary_regressions_C},
Figure~\ref{fig:summary_regressions_D},
Figure~\ref{fig:summary_regressions_E},
Figure~\ref{fig:summary_regressions_F},
Figure~\ref{fig:summary_regressions_G},
Figure~\ref{fig:summary_regressions_H}, and
Figure~\ref{fig:summary_regressions_A} for more details.
\michael{Put a bit of discussion, e.g., on best and worst.}

@@

\input{figs_largeScale_A}
\input{figs_largeScale_B}
\input{figs_largeScale_C}
\input{figs_largeScale_D}
\input{figs_largeScale_E}
\input{figs_largeScale_F}
\input{figs_largeScale_G}
\input{figs_largeScale_H}
\input{figs_largeScale_I}

@@
